E~1~: Laws predict deteriorating human rights

### 2021-04-04 analysis/02_descriptive-analysis.Rmd
PHEWWWW ALL READY FOR ISA

```{r make-map-data}
things_to_map <- canary %>% 
  filter(year %in% c(1990, 2013)) %>% 
  select(country, year, iso3, barriers_total, PTS_factor, v2csreprss) %>% 
  pivot_wider(names_from = year, values_from = c(barriers_total, PTS_factor, v2csreprss)) %>% 
  mutate(new_laws = barriers_total_2013 - barriers_total_1990,
         new_laws = ifelse(new_laws <= 0, 0, new_laws),
         new_laws = ceiling(new_laws)) %>% 
  mutate(diff_csrepress = v2csreprss_2013 - v2csreprss_1990,
         diff_csrepress_trunc = case_when(
           diff_csrepress >= 2 ~ 2,
           diff_csrepress <= -2 ~ -2,
           TRUE ~ diff_csrepress
         )) %>% 
  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_1990,
         pct_change_csrepress_trunc = case_when(
           pct_change_csrepress >= 5 ~ 5,
           pct_change_csrepress <= -5 ~ -5,
           TRUE ~ pct_change_csrepress
         ))

@@

```{r map-ngo-laws}
map_ngo_laws <- ggplot() +
  geom_sf(data = map_data, aes(fill = factor(new_laws)),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 8)), 
                    na.value = "grey80", breaks = 0:6) +
  # scale_fill_manual(values = scico(7, palette = "devon", direction = -1), 
  #                   na.value = "grey80", breaks = 0:6) +
  guides(fill = guide_legend(nrow = 1, label.position = "bottom",
                             keywidth = unit(1, units = "lines"),
                             keyheight = unit(0.6, units = "lines"))) +
  labs(fill = "Restrictive NGO laws passed between 1990 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.spacing.x = unit(0, "pt"),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(10, "lines"),
                                              padding = margin(r = 10)))
map_ngo_laws
```

>>>>

```{r make-map-data}
things_to_map <- canary %>% 
  filter(year %in% c(1993, 2013)) %>% 
  select(country, year, iso3, barriers_total, PTS_factor, v2csreprss) %>% 
  pivot_wider(names_from = year, values_from = c(barriers_total, PTS_factor, v2csreprss)) %>% 
  mutate(new_laws = barriers_total_2013 - barriers_total_1993,
         new_laws = ifelse(new_laws <= 0, 0, new_laws),
         new_laws = ceiling(new_laws),
         new_laws_cat = ifelse(new_laws >= 5, "5+", as.character(new_laws))) %>% 
  mutate(diff_csrepress = v2csreprss_2013 - v2csreprss_1993,
         diff_csrepress_trunc = case_when(
           diff_csrepress >= 2 ~ 2,
           diff_csrepress <= -2 ~ -2,
           TRUE ~ diff_csrepress
         )) %>% 
  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_1993,
         pct_change_csrepress_trunc = case_when(
           pct_change_csrepress >= 5 ~ 5,
           pct_change_csrepress <= -5 ~ -5,
           TRUE ~ pct_change_csrepress
         ))

@@

```{r map-ngo-laws}
map_ngo_laws <- ggplot() +
  geom_sf(data = map_data, aes(fill = factor(new_laws_cat)),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#CF4446")(seq(0, 1, length.out = 6)),
                    na.value = "grey95", breaks = c(as.character(0:4), "5+")) +
  # scale_fill_manual(values = scico(7, palette = "devon", direction = -1),
  #                   na.value = "grey80", breaks = 0:6) +
  guides(fill = guide_legend(nrow = 1, label.position = "bottom",
                             keywidth = unit(1, units = "lines"),
                             keyheight = unit(0.6, units = "lines"))) +
  labs(fill = "Restrictive NGO laws passed between 1993 and 2013") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.spacing.x = unit(0, "pt"),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(10, "lines"),
                                              padding = margin(r = 10)))
map_ngo_laws
```

### 2021-04-04 analysis/03_laws-repression.Rmd
PHEWWWW ALL READY FOR ISA

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted civil liberties index\n(higher values = less violence)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

>>>>

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted civil liberties index\n(higher values = better protection)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```
